\LARGE \bf Longitudinal Trajectory Planning and Tracking for Fixed-Path Autonomous Driving

### 2016-01-13 paper1.tex
started first paragraph of tracking section

% Need some lead in here?
% \subsection{Simple Case}

@@

% make sure to incorporate extensibility to other constraints
The goal of the segmentation process is to divide a given path into multiple portions where each has a uniform upper limit on speed, acceleration, and braking.
There are 3 steps in the segmentation process:
\begin{enumerate}
  \item \emph{Ceiling calculation}, where $\bf{b}$, $\bf{a}_m$, and $\bf{j}_m$ are found for every point in the given path.
  \item \emph{Clustering}, in which path points are grouped sequentially.
  \item \emph{Consolidation}, in which a single $\bf{b}$, $\bf{a}_m$, and $\bf{j}_m$ is selected for each segment.
\end{enumerate}
After this is done, the process described above in Section \ref{sec:jerkprofiles} may be applied to each of the segments.

@@

This information is used to choose the segment boundaries in the clustering step.
Any number of clustering algorithms may be used here, and prudent choice of segment boundaries is arguably one of the most critical pieces of trajectory planning process.
For the present example, we will choose a simple univariate heuristic which essentially identifies curves in the roadway.
Each time that $v_{m,k} < SL$ becomes true, a curve is beginning, and a segment boundary is drawn.
Each time that $v_{m,k} = SL$ is once again true, the current curve has ended, and another segment boundary is drawn.
Figure~\ref{fig:course_highlight_turns} shows the result of this algorithm.

\begin{figure}[thpb]
  \label{fig:course_highlight_turns}
  \centering
  \includegraphics[width=\columnwidth]{graphics/course_highlighted_turns.png}
  \caption{Clustering output for a short path when using an algorithm which draws segment boundaries around curves.}
\end{figure}

In the consolidation step, ...

\begin{figure}[thpb]
  \label{fig:consolidation_speed_ceiling}
  \centering
  \includegraphics[width=\columnwidth]{graphics/speed_ceiling.png}
\end{figure}

@@

asdf

@@

Thanks.

>>>>

@@

% make sure to incorporate extensibility to other constraints
The goal of the segmentation process is to divide a given path into multiple portions where each has a uniform upper limit on speed, acceleration, and braking.
There are 3 steps in the segmentation process:
\begin{enumerate} \label{asdf}
  \item \emph{Ceiling calculation}, where $\bf{b}$, $\bf{a}_m$, and $\bf{j}_m$ are found for every point in the given path.
  \item \emph{Clustering}, in which path points are grouped sequentially.
  \item \emph{Consolidation}, in which a single $\bf{b}$, $\bf{a}_m$, and $\bf{j}_m$ is selected for each segment.
\end{enumerate}
After this is done, the process described above in Section \ref{sec:jerkprofiles} may be applied to each of the segments.

@@

This information is used to choose the segment boundaries in the clustering step.
Any number of clustering algorithms may be used here, and prudent choice of segment boundaries is arguably one of the most critical pieces of trajectory planning process.
For the present example, we will choose a simple univariate heuristic which essentially identifies curves in the roadway.
Each time that $v_{m,k} < SL$ becomes true, a curve is beginning, and a segment boundary is drawn.
Each time that $v_{m,k} = SL$ is once again true, the current curve has ended, and another segment boundary is drawn.
Figure \ref{fig:course_highlight_turns} shows the result of this algorithm.

\begin{figure}[thpb]
  \centering
  \includegraphics[width=\columnwidth]{graphics/course_highlighted_turns.png}
  \caption{Clustering output for a short path when using an algorithm which draws segment boundaries around curves.}
  \label{fig:course_highlight_turns}
\end{figure}

In the consolidation step, a single $\bf{g}$ must be calculated for each segment using the values of $\bf{g}$ corresponding to each of the path points which comprise the segment in question.

\begin{figure}[thpb]
  \centering
  \includegraphics[width=\columnwidth]{graphics/speed_ceiling.png}
  \caption{Example of $v_m$ consolidation for simple univariate path clustering.}
  \label{fig:consolidation_speed_ceiling}
\end{figure}

@@

After planning has been performed, a reference signal must be regularly supplied to a control system in order for the vehicle to carry out the plan.
This is known as tracking.
The primary difficulty here is that the trajectory plan has been developed in a one dimensional position space using a reference time which will have unknown drift relative to real time.
As such, we must find some way to look up the coordinates of the vehicle within the reference trajectory using information typically available for autonomous cars.
A minimal set of such information would include position, velocity vector, heading, and acceleration in the body frame.
After this, it is assumed that the vehicle controller will need samples of a small window into the future trajectory in order to pilot the vehicle.

@@

Thanks...
